\documentclass[12pt,letterpaper, onecolumn]{exam}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[lmargin=71pt, tmargin=1.2in]{geometry}
\thispagestyle{empty}

\begin{document}

\begingroup  
    \centering
    \LARGE Linear Algebra\\[0.5em]
    \LARGE Assignment 3\\[0.5em]
    \large Due Sunday at 11:59 PM\par
\endgroup
\rule{\textwidth}{0.4pt}

\begin{questions}

    \question Directions
    Complete the following problems showing all your work. You may use a calculator to check your work, but should write
    out (or TeX up) all the steps of your solution. Unless otherwise specified, you may skip some steps of row reduction with a
    calculator, but state that you did so. Please upload your work as a single .pdf file in Blackboard.

    \question Problems
    \begin{parts}
        \part Which of the following are linear transformations? For each problem below, first determine if the transformation is
        linear or not. Then, for each linear transformation, write the standard matrix of the transformation. When showing a
        transformation is not linear, provide a specific reason or counterexample.
        \begin{enumerate}
            \item Reflection about the $x$-axis in $\mathbb{R}^2$.
            \item Reflection about the line $x = 1$ in $\mathbb{R}^2$.
            \item Translation $T_{\vec{v}} : \mathbb{R}^2 \rightarrow \mathbb{R}^2$ by a nonzero vector $\vec{v}$ in $\mathbb{R}^2$. (i.e., $T(\vec{x}) = \vec{x} + \vec{v}$)
            \item $T(x) = x^2$ in $\mathbb{R}$.
            \item For each vector $\vec{v} = \begin{bmatrix} a \\ b \\ c \\ d \end{bmatrix} \in \mathbb{R}^4$, associate to it the cubic polynomial $f(x) = ax^3 + bx^2 + cx + d$. Then consider the
            transformation $T(f) = f'$, where $f'(x)$ is the derivative.
        \end{enumerate}

        \part In the (sadly fictitious) suspense movie, \textit{The Linear Combination}, our three main characters Adam, Bob and Carl
        have each been mailed a mysterious letter directing them to a combination safe and promising that its contents are of
        extreme value. They were told that there is a linear transformation $T: \mathbb{R}^3 \rightarrow \mathbb{R}^3$ and that the combination to the safe
        is a three-digit number corresponding to the vector $T\begin{pmatrix} 4 \\ 4 \\ 15 \end{pmatrix}$. In their letters, each was given partial information about
        $T$.
        Adam knows $T\begin{pmatrix} 1 \\ 0 \\ 1 \end{pmatrix} = \begin{pmatrix} 2 \\ 1 \\ 0 \end{pmatrix}$, Bob knows $T\begin{pmatrix} 1 \\ 2 \\ 3 \end{pmatrix} = \begin{pmatrix} 0 \\ 1 \\ 1 \end{pmatrix}$, and Carl knows $T\begin{pmatrix} 0 \\ 0 \\ 7 \end{pmatrix} = \begin{pmatrix} 1 \\ 1 \\ 0 \end{pmatrix}$.
        \begin{enumerate}
            \item Explain why, if Adam, Bob and Carl work together, they can determine the combination to the safe. Also,
            determine the combination to the safe.
            \item Explain why, if Bob and Carl work together but they \textit{don't} work with Adam, they won't have enough information
            to determine the combination.
            \item Explain why, if the combination to the safe was the vector $T\begin{pmatrix} 2 \\ 4 \\ -1 \end{pmatrix}$, Bob and Carl could have determined the
            combination without Adam's help.
        \end{enumerate}
    \end{parts}
\end{questions}
\end{document}